### 2013-06-30 Rcode/intro.rmd
minor update

Note that to compare ash $q$ values with fdr-type $q$ values we
multiply them by 2 (this is because the ash $q$ values indicate the
probability of an error of sign, which is half as large as the
probability of a false discovery: half the false discoveries would
have the right sign by random guessing)
```{r}
plot(qval$q,2*beta.ash$qval,main="comparison of ash and q value qvalues",xlab="qvalue", ylab="twice ash q values")
abline(a=0,b=1)
```

>>>>

#### Comparison with qvalue

Here we compare ash $q$ values with those from the qvalue package. Because of the issue above, we multiply the ash  $q$ values by 2.
```{r}
plot(qval$q,2*beta.ash$qval,main="comparison of ash and q value qvalues",xlab="qvalue", ylab="twice ash q values")
abline(a=0,b=1)
```
